PANCHANGE_data_preprocessing

### 2020-07-22 PANCHANGE_data_preprocessing2020-07-15.Rmd
Reviewed GLAD PCL cleaning and scoring

```{r coping glad pcl cleaning}
coping.glad.pcl.raw.id <- coping.glad.pcl.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID),
         startDate.glad = startDate) %>% # Rename startDate
  select(
    Sample, # Sample
    ID, # ID
    pcl.stressful_experience_repeated_images_base_numeric = pcl6.stressful_experience_repeated_images_numeric,
    pcl.stressful_experience_repeated_images_base = pcl6.stressful_experience_repeated_images,
    pcl.stressful_experience_upset_reminded_base_numeric = pcl6.stressful_experience_upset_reminded_numeric,
    pcl.stressful_experience_upset_reminded_base = pcl6.stressful_experience_upset_reminded,
    pcl.stressful_situation_avoiding_activities_base_numeric = pcl6.avoiding_activities_stressful_experience_numeric, # differ to GLAD prepan
    pcl.stressful_situation_avoiding_activities_base = pcl6.avoiding_activities_stressful_experience, # differ to GLAD prepan
    pcl.cut_people_feeling_distant_base_numeric = pcl6.cut_people_feeling_distant_numeric,
    pcl.cut_people_feeling_distant_base = pcl6.cut_people_feeling_distant,
    pcl.feeling_irritable_or_having_angry_outbursts_base_numeric = pcl6.feeling_irritable_or_having_angry_outbursts_numeric,
    pcl.feeling_irritable_or_having_angry_outbursts_base = pcl6.feeling_irritable_or_having_angry_outbursts,
    pcl.difficulty_concentrating_base_numeric = pcl6.difficulty_concentrating_numeric,
    pcl.difficulty_concentratin_base = pcl6.difficulty_concentrating,
    pcl.stressful_experience_repeated_images_retro_numeric = pcl6.stressful_experience_repeated_images.1_numeric,
    pcl.stressful_experience_repeated_images_retro = pcl6.stressful_experience_repeated_images.1,
    pcl.stressful_experience_upset_reminded_retro_numeric = pcl6.stressful_experience_upset_reminded.1_numeric,
    pcl.stressful_experience_upset_reminded_retro = pcl6.stressful_experience_upset_reminded.1,
    pcl.stressful_situation_avoiding_activities_retro_numeric = pcl6.avoiding_activities_stressful_experience.1_numeric,
    pcl.stressful_situation_avoiding_activities_retro = pcl6.avoiding_activities_stressful_experience.1,
    pcl.cut_people_feeling_distant_retro_numeric = pcl6.cut_people_feeling_distant.1_numeric,
    pcl.cut_people_feeling_distant_retro = pcl6.cut_people_feeling_distant.1,
    pcl.feeling_irritable_or_having_angry_outbursts_retro_numeric = pcl6.feeling_irritable_or_having_angry_outbursts.1_numeric,
    pcl.feeling_irritable_or_having_angry_outbursts_retro = pcl6.feeling_irritable_or_having_angry_outbursts.1,
    pcl.difficulty_concentrating_retro_numeric = pcl6.difficulty_concentrating.1_numeric,
    pcl.difficulty_concentratin_retro = pcl6.difficulty_concentrating.1
  ) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

@@

Calculate sum score for PHQ-9 retro
```{r coping pcl sum score retro}
# Create vector with scoring key: If the item is reversed coded use -1. 
# There needs to be the correct number of values for each item in the questionnaire. 
pcl.items_key_retro <- c(1,1,1,1,1,1)

@@

Calculate sum score for PHQ-9 base
```{r coping pcl sum score base}
# Create vector with scoring key: If the item is reversed coded use -1. 
# There needs to be the correct number of values for each item in the questionnaire. 
pcl.items_key_base <- c(1,1,1,1,1,1)

>>>>

```{r coping glad pcl cleaning}
coping.glad.pcl.raw.id <- coping.glad.pcl.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID),
         startDate.glad = startDate) %>% # Rename startDate
  select(
    Sample, # Sample
    ID, # ID
    pcl.stressful_experience_repeated_images_base_numeric = pcl6.stressful_experience_repeated_images_numeric,
    pcl.stressful_experience_repeated_images_base = pcl6.stressful_experience_repeated_images,
    pcl.stressful_experience_upset_reminded_base_numeric = pcl6.stressful_experience_upset_reminded_numeric,
    pcl.stressful_experience_upset_reminded_base = pcl6.stressful_experience_upset_reminded,
    pcl.stressful_situation_avoiding_activities_base_numeric = pcl6.avoiding_activities_stressful_experience_numeric, # differ to GLAD prepan
    pcl.stressful_situation_avoiding_activities_base = pcl6.avoiding_activities_stressful_experience, # differ to GLAD prepan
    pcl.cut_people_feeling_distant_base_numeric = pcl6.cut_people_feeling_distant_numeric,
    pcl.cut_people_feeling_distant_base = pcl6.cut_people_feeling_distant,
    pcl.feeling_irritable_or_having_angry_outbursts_base_numeric = pcl6.feeling_irritable_or_having_angry_outbursts_numeric,
    pcl.feeling_irritable_or_having_angry_outbursts_base = pcl6.feeling_irritable_or_having_angry_outbursts,
    pcl.difficulty_concentrating_base_numeric = pcl6.difficulty_concentrating_numeric,
    pcl.difficulty_concentratin_base = pcl6.difficulty_concentrating,
    pcl.stressful_experience_repeated_images_retro_numeric = pcl6.stressful_experience_repeated_images.1_numeric,
    pcl.stressful_experience_repeated_images_retro = pcl6.stressful_experience_repeated_images.1,
    pcl.stressful_experience_upset_reminded_retro_numeric = pcl6.stressful_experience_upset_reminded.1_numeric,
    pcl.stressful_experience_upset_reminded_retro = pcl6.stressful_experience_upset_reminded.1,
    pcl.stressful_situation_avoiding_activities_retro_numeric = pcl6.avoiding_activities_stressful_experience.1_numeric,
    pcl.stressful_situation_avoiding_activities_retro = pcl6.avoiding_activities_stressful_experience.1,
    pcl.cut_people_feeling_distant_retro_numeric = pcl6.cut_people_feeling_distant.1_numeric,
    pcl.cut_people_feeling_distant_retro = pcl6.cut_people_feeling_distant.1,
    pcl.feeling_irritable_or_having_angry_outbursts_retro_numeric = pcl6.feeling_irritable_or_having_angry_outbursts.1_numeric,
    pcl.feeling_irritable_or_having_angry_outbursts_retro = pcl6.feeling_irritable_or_having_angry_outbursts.1,
    pcl.difficulty_concentrating_retro_numeric = pcl6.difficulty_concentrating.1_numeric,
    pcl.difficulty_concentrating_retro = pcl6.difficulty_concentrating.1
  ) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

@@

Calculate sum score for PCL-6 retro
```{r coping pcl sum score retro}
# Create vector with scoring key: If the item is reversed coded use -1. 
# There needs to be the correct number of values for each item in the questionnaire. 
pcl.items_key_retro <- c(1,1,1,1,1,1)

@@

Calculate sum score for PCL-6 base
```{r coping pcl sum score base}
# Create vector with scoring key: If the item is reversed coded use -1. 
# There needs to be the correct number of values for each item in the questionnaire. 
pcl.items_key_base <- c(1,1,1,1,1,1)
